Digitization of the Australian Parliamentary Debates, 1998-2022

### 2023-07-05 paper/paper-nature-revised.qmd
paper and script updates

This section is structured as follows. First, we provide an overview of our approach to understanding and parsing an individual Hansard XML document, which informed the scripts used to create our database. This will be supplemented with an excerpt from a Hansard XML to provide a visual example of its structure. Next we will explain the specific differences between the scripts, and outline what structural changes necessitated their separate development. We then provide details on the methodological intricacies of three core components of Hansard proceedings: Question Time, interjections, and stage directions. Further, we discuss the script we developed to fill in remaining missing details on the MP speaking, which each file in our database was passed to after being parsed and cleaned. **Finally, we review the supplementary Hansard debate topics dataset we created to expand the versatility of our database.**

@@

@@

**Finally, there is a CSV file in our database called `PartyFacts_map.csv`. This file was created using `AustralianPoliticians` data, data downloaded from the Party Facts project, and our own Hansard data `party` variable. As there are some party name and abbreviation spelling inconsistencies across these sources, creating this dataframe allowed us to ensure correct merging of PartyFacts ID numbers with their associated party, in accordance with the party abbreviation spelling transcribed in our Hansard data. Further, we included the corresponding party abbreviation and full name spelling found in the `AustralianPoliticians` package for completeness.**

@@

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: tbl-speeches_by_party
#| tbl-cap: "Total number of speeches made in our database by political party"
read_csv("s_by_party_name.csv", show_col_types = F) |> 
  knitr::kable(booktabs=T) |> 
  kableExtra::kable_styling(full_width = F, latex_options = "HOLD_position")
#### check NAT vs NPA full names - are these correct? google is confusing me
```

>>>>

This section is structured as follows. First, we provide an overview of our approach to understanding and parsing an individual Hansard XML document, which informed the scripts used to create our database. This will be supplemented with an excerpt from a Hansard XML to provide a visual example of its structure. Next we will explain the specific differences between the scripts, and outline what structural changes necessitated their separate development. We then provide details on the methodological intricacies of three core components of Hansard proceedings: Question Time, interjections, and stage directions. Further, we discuss the script we developed to fill in remaining missing details on the MP speaking, which each file in our database was passed to after being parsed and cleaned. **Finally, we review the supplementary Hansard debate topics dataset and supplementary divisions dataset we created to expand the versatility of our database.**

@@

## Divisions

**Another fundamental component of parliamentary proceedings is voting. In the House, when a question arises such as “The question is that the amendment be agreed to”, Members are asked to cast their vote either in the affirmative or in the negative, and the majority of votes as judged by the Speaker determines the outcome [@australia2018house]. Further, Members can vote in an unofficial arrangement called pairs, in which as written in Chapter 8 of @australia2018house, "can be used to enable a Member on one side of the House to be absent for any votes when a Member from the other side is to be absent at the same time or when, by agreement, a Member abstains from voting". If the result as determined by the Speaker is challenged by more than one MP, this leads to a division of the House in which the question is re-stated and Members must move to the left or right of their chair depending on how they vote, so that the votes can be re-counted and recorded [@australia2018house].**

**In the Hansard XML files, divisions data are structured outside of the `<speech>` content in their own `<division>` nodes that contain the voting data and division result. Since we focus primarily on the spoken `<speech>` Hansard content, our parsing scripts do not necessarily capture all divisions data from House proceedings. Our approach to parsing Hansard in the third and fourth scripts described in @sec-diff naturally allowed for much of the divisions data to be added to our resulting files for 1998 to March 2011, however the parsing scripts used for May 2011 to September 2022 Hansard did not. To supplement our database and in an effort to fill this divisions data gap, we created an additional file containing all divisions data nested under the XPath "`//chamber.xscript//division`" from the Hansard files in our time frame. To produce this data file, for each Hansard XML we parsed the `<division.header>`, `<division.data>`, and `<division.result>` child-nodes where they existed, extracted any time stamps where available, and did any additional data cleaning as necessary. We used a series of if-else statements in this script to account for variation in the structure of the `<divisions>` node over time. Finally, we then added a date variable to distinguish between sitting days.**

@@

**There is also a CSV file in our database called `PartyFacts_map.csv`. This file was created using `AustralianPoliticians` data, data downloaded from the Party Facts project, and our own Hansard data `party` variable. As there are some party name and abbreviation spelling inconsistencies across these sources, creating this dataframe allowed us to ensure correct merging of PartyFacts ID numbers with their associated party, in accordance with the party abbreviation spelling transcribed in our Hansard data. Further, we included the corresponding party abbreviation and full name spelling found in the `AustralianPoliticians` package for completeness.**

@@

**Finally, our database contains a file with all parsed divisions data in our timeframe. This is called `division_data`, and is available in RDA form and in Parquet form. The reason it is not available in CSV form is because three of the variables (`names_AYES`, `names_NOES`, and `names_PAIRS`) are lists, which are not supported by the CSV rectangular data structure. The variables found in these data are summarized below, in @tbl-divisions.**

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: tbl-divisions
#| tbl-cap: "Summary and description of variables in our divisions data file"
tibble("Variable" = c("date",
                      "div_num",
                      "time.stamp",
                      "num.votes_AYES",
                      "num.votes_NOES",
                      "num.votes_PAIRS",
                      "names_AYES",
                      "names_NOES",
                      "names_PAIRS",
                      "result"),
       "Description" = c("Sitting day",
                         "Index for each division parsed for that sitting day",
                         "Time stamp associated with each division",
                         "Number of votes in the affirmative",
                         "Number of votes in the negative",
                         "Number of votes in pairs",
                         "List of the names of Members who voted in the affirmative",
                         "List of the names of Members who voted in the negative",
                         "List of the names of Members who votes in pairs",
                         "Voting result")) |> 
  kable(booktabs=T) %>% 
  kableExtra::kable_styling(full_width = F, latex_options = "HOLD_position")
```

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: tbl-speeches_by_party
#| tbl-cap: "Total number of speeches made in our database by political party"
read_csv("s_by_party_name.csv", show_col_types = F) |> 
  knitr::kable(booktabs=T) |> 
  kableExtra::kable_styling(full_width = F, latex_options = "HOLD_position")
```

### 2023-07-05 paper/paper-nature-revised.tex
paper and script updates

\title{Digitization of the Australian Parliamentary Debates, 1998-2022}
\author{Lindsay Katz\footnote{University of Toronto,
  lindsay.katz@mail.utoronto.ca} \and Rohan Alexander\footnote{University
  of Toronto, rohan.alexander@utoronto.ca}}
\date{July 4, 2023}

\begin{document}
\maketitle
\begin{abstract}
Public knowledge of what is said in parliament is a tenet of democracy,
and a critical resource for political science research. In Australia,
following the British tradition, the written record of what is said in
parliament is known as Hansard. While the Australian Hansard has always
been publicly available, it has been difficult to use for the purpose of
large-scale macro- and micro-level text analysis because it has only
been available as PDFs or XMLs. Following the lead of the Linked
Parliamentary Data project which achieved this for Canada, we provide a
new, comprehensive, high-quality, rectangular database that captures
proceedings of the Australian parliamentary debates from 1998 to 2022.
The database is publicly available and can be linked to other datasets
such as election results. The creation and accessibility of this
database enables the exploration of new questions and serves as a
valuable resource for both researchers and policymakers.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, borderline west={3pt}{0pt}{shadecolor}, breakable, sharp corners, boxrule=0pt, interior hidden, frame hidden]}{\end{tcolorbox}}\fi

@@

This section is structured as follows. First, we provide an overview of
our approach to understanding and parsing an individual Hansard XML
document, which informed the scripts used to create our database. This
will be supplemented with an excerpt from a Hansard XML to provide a
visual example of its structure. Next we will explain the specific
differences between the scripts, and outline what structural changes
necessitated their separate development. We then provide details on the
methodological intricacies of three core components of Hansard
proceedings: Question Time, interjections, and stage directions.
Further, we discuss the script we developed to fill in remaining missing
details on the MP speaking, which each file in our database was passed
to after being parsed and cleaned. \textbf{Finally, we review the
supplementary Hansard debate topics dataset we created to expand the
versatility of our database.}

@@

@@

\textbf{Finally, there is a CSV file in our database called
\texttt{PartyFacts\_map.csv}. This file was created using
\texttt{AustralianPoliticians} data, data downloaded from the Party
Facts project, and our own Hansard data \texttt{party} variable. As
there are some party name and abbreviation spelling inconsistencies
across these sources, creating this dataframe allowed us to ensure
correct merging of PartyFacts ID numbers with their associated party, in
accordance with the party abbreviation spelling transcribed in our
Hansard data. Further, we included the corresponding party abbreviation
and full name spelling found in the \texttt{AustralianPoliticians}
package for completeness.}

@@

@@

\centering
\begin{tabular}{llr}
\toprule
Party Name & Party Abbreviation & Total \# of Speeches\\
\midrule
Australian Labor Party & ALP & 112268\\
Liberal Party of Australia & LIB & 106139\\
Nationalist Party & NAT & 15799\\
Independent & IND & 5357\\
National Party of Australia & NPA & 4580\\
\addlinespace
Australian Greens & GRN & 1446\\
Country Liberal Party (Northern Territory) & CLP & 665\\
Centre Alliance & CA & 638\\
Katters Australian Party & KAP & 263\\
Nick Xenophon Team & NXT & 186\\
\addlinespace
National Party of Australia (WA) & NATS WA & 68\\
Palmer United Party & PUP & 64\\
United Australia Party & UAP & 43\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\title{Digitization of the Australian Parliamentary Debates, 1998-2022}
\author{Lindsay Katz\footnote{University of Toronto,
  lindsay.katz@mail.utoronto.ca} \and Rohan Alexander\footnote{University
  of Toronto, rohan.alexander@utoronto.ca}}
\date{July 5, 2023}

\begin{document}
\maketitle
\begin{abstract}
Public knowledge of what is said in parliament is a tenet of democracy,
and a critical resource for political science research. In Australia,
following the British tradition, the written record of what is said in
parliament is known as Hansard. While the Australian Hansard has always
been publicly available, it has been difficult to use for the purpose of
large-scale macro- and micro-level text analysis because it has only
been available as PDFs or XMLs. Following the lead of the Linked
Parliamentary Data project which achieved this for Canada, we provide a
new, comprehensive, high-quality, rectangular database that captures
proceedings of the Australian parliamentary debates from 1998 to 2022.
The database is publicly available and can be linked to other datasets
such as election results. The creation and accessibility of this
database enables the exploration of new questions and serves as a
valuable resource for both researchers and policymakers.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, frame hidden, enhanced, breakable, sharp corners, boxrule=0pt, interior hidden]}{\end{tcolorbox}}\fi

@@

This section is structured as follows. First, we provide an overview of
our approach to understanding and parsing an individual Hansard XML
document, which informed the scripts used to create our database. This
will be supplemented with an excerpt from a Hansard XML to provide a
visual example of its structure. Next we will explain the specific
differences between the scripts, and outline what structural changes
necessitated their separate development. We then provide details on the
methodological intricacies of three core components of Hansard
proceedings: Question Time, interjections, and stage directions.
Further, we discuss the script we developed to fill in remaining missing
details on the MP speaking, which each file in our database was passed
to after being parsed and cleaned. \textbf{Finally, we review the
supplementary Hansard debate topics dataset and supplementary divisions
dataset we created to expand the versatility of our database.}

@@

\hypertarget{divisions}{%
\subsection{Divisions}\label{divisions}}

\textbf{Another fundamental component of parliamentary proceedings is
voting. In the House, when a question arises such as ``The question is
that the amendment be agreed to'', Members are asked to cast their vote
either in the affirmative or in the negative, and the majority of votes
as judged by the Speaker determines the outcome\textsuperscript{3}.
Further, Members can vote in an unofficial arrangement called pairs, in
which as written in Chapter 8 of\textsuperscript{3}, ``can be used to
enable a Member on one side of the House to be absent for any votes when
a Member from the other side is to be absent at the same time or when,
by agreement, a Member abstains from voting''. If the result as
determined by the Speaker is challenged by more than one MP, this leads
to a division of the House in which the question is re-stated and
Members must move to the left or right of their chair depending on how
they vote, so that the votes can be re-counted and
recorded\textsuperscript{3}.}

\textbf{In the Hansard XML files, divisions data are structured outside
of the \texttt{\textless{}speech\textgreater{}} content in their own
\texttt{\textless{}division\textgreater{}} nodes that contain the voting
data and division result. Since we focus primarily on the spoken
\texttt{\textless{}speech\textgreater{}} Hansard content, our parsing
scripts do not necessarily capture all divisions data from House
proceedings. Our approach to parsing Hansard in the third and fourth
scripts described in Section~\ref{sec-diff} naturally allowed for much
of the divisions data to be added to our resulting files for 1998 to
March 2011, however the parsing scripts used for May 2011 to September
2022 Hansard did not. To supplement our database and in an effort to
fill this divisions data gap, we created an additional file containing
all divisions data nested under the XPath
``\texttt{//chamber.xscript//division}'' from the Hansard files in our
time frame. To produce this data file, for each Hansard XML we parsed
the \texttt{\textless{}division.header\textgreater{}},
\texttt{\textless{}division.data\textgreater{}}, and
\texttt{\textless{}division.result\textgreater{}} child-nodes where they
existed, extracted any time stamps where available, and did any
additional data cleaning as necessary. We used a series of if-else
statements in this script to account for variation in the structure of
the \texttt{\textless{}divisions\textgreater{}} node over time. Finally,
we then added a date variable to distinguish between sitting days.}

@@

\textbf{There is also a CSV file in our database called
\texttt{PartyFacts\_map.csv}. This file was created using
\texttt{AustralianPoliticians} data, data downloaded from the Party
Facts project, and our own Hansard data \texttt{party} variable. As
there are some party name and abbreviation spelling inconsistencies
across these sources, creating this dataframe allowed us to ensure
correct merging of PartyFacts ID numbers with their associated party, in
accordance with the party abbreviation spelling transcribed in our
Hansard data. Further, we included the corresponding party abbreviation
and full name spelling found in the \texttt{AustralianPoliticians}
package for completeness.}

@@

\textbf{Finally, our database contains a file with all parsed divisions
data in our timeframe. This is called \texttt{division\_data}, and is
available in RDA form and in Parquet form. The reason it is not
available in CSV form is because three of the variables
(\texttt{names\_AYES}, \texttt{names\_NOES}, and \texttt{names\_PAIRS})
are lists, which are not supported by the CSV rectangular data
structure. The variables found in these data are summarized below, in
Table~\ref{tbl-divisions}.}

\hypertarget{tbl-divisions}{}
\begin{table}[H]
\caption{\label{tbl-divisions}Summary and description of variables in our divisions data file }\tabularnewline

\centering
\begin{tabular}{ll}
\toprule
Variable & Description\\
\midrule
date & Sitting day\\
div\_num & Index for each division parsed for that sitting day\\
time.stamp & Time stamp associated with each division\\
num.votes\_AYES & Number of votes in the affirmative\\
num.votes\_NOES & Number of votes in the negative\\
\addlinespace
num.votes\_PAIRS & Number of votes in pairs\\
names\_AYES & List of the names of Members who voted in the affirmative\\
names\_NOES & List of the names of Members who voted in the negative\\
names\_PAIRS & List of the names of Members who votes in pairs\\
result & Voting result\\
\bottomrule
\end{tabular}
\end{table}

@@

\centering
\begin{tabular}{llr}
\toprule
Party Name & Party Abbreviation & Total \# of Speeches\\
\midrule
Australian Labor Party & ALP & 112268\\
Liberal Party of Australia & LIB & 106139\\
National Party of Australia & NPA & 20244\\
Independent & IND & 5357\\
Australian Greens & GRN & 1446\\
\addlinespace
Country Liberal Party (Northern Territory) & CLP & 665\\
Centre Alliance & CA & 638\\
Katters Australian Party & KAP & 263\\
Nick Xenophon Team & NXT & 186\\
National Party of Australia (WA) & NATS WA & 68\\
\addlinespace
Palmer United Party & PUP & 64\\
United Australia Party & UAP & 43\\
\bottomrule
\end{tabular}
\end{table}
